\documentclass[12pt,a4paper]{article}
\begin{document}

\title{Ergodicity economics: lecture plan}
\author{Ole Peters \& Alexander Adamou}
\date{\today}
\maketitle

\section*{Tools}
\subsection*{Lecture 1}
Coin game. Random variable. Expectation value. Ensemble average.

\subsection*{Lecture 2}
Stochastic process. Time average. Ergodicity.

\subsection*{Lecture 3}
Random walk. Brownian motion. Stochastic differential equations.

\subsection*{Lecture 4}
Geometric Brownian motion. It\^{o} calculus.

\section*{Microeconomics}
\subsection*{Lecture 5}
Decisions in a riskless world.
Growth rates (additive, multiplicative, general).

\subsection*{Lecture 6}
Decisions in a riskless world.
Discounting, preference reversal, impatience and poverty.

\subsection*{Lecture 7}
Decisions in a risky world.
Perturbed dynamics (additive, multiplicative, general), growth rate is ergodic. EE decision model.

\subsection*{Lecture 8}
Decisions in a risky world.
Gambles (random number and duration) as pieces of stochastic processes, expected wealth and expected utility, ergodicity transformation and corresponding wealth process -- Ito.

\subsection*{Lecture 9}
Decisions in the real world.
St. Petersburg paradox, Copenhagen experiment, insurance.

\subsection*{Lecture 10}
Decisions in the real world (previous 2 lectures may not get finished).

\section*{Macroeconomics}
\subsection*{Lecture 11}
Lognormal distribution. Two growth rates. Measuring inequality. Condensation.

\subsection*{Lecture 12}
Rescaled wealth. Dynamics and distributions. Jensen's inequality. Power laws.

\subsection*{Lecture 13}
Sums of lognormals. Random energy model.

\subsection*{Lecture 14}
Farmer's fable. Cooperation in GBM. Correlated fluctuations. Idiosyncratic parameters.

\subsection*{Lecture 15}
Reallocating GBM. Model regimes. Inverse gamma distribution.

\subsection*{Lecture 16}
Ergodic hypothesis. US wealth data.

\subsection*{Lecture 17}
A two-asset market, portfolio theory: Markowitz, Sharpe ratio, expected return, growth rate optimization, optimal leverage.

\subsection*{Lecture 18}
Stochastic market efficiency: efficiency, stability, predictions and accuracy.

\subsection*{Lecture 19}
Stochastic market efficiency: a theory of noise, equity premium puzzle solution, central bank interest rates, fraud detection.

\subsection*{Lecture 20}
Stochastic market efficiency: real markets. Backtests of constant-leverage investments, SP500, Dax, Bitcoin, Madoff; full time series and expanding windows, typicality.

\end{document}